---
title: "Project 3: Stat302.Proj3 Tutorial"
author: "Qiiaozhi Fu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Stat302.Proj3 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Stat302.Proj3)
```

```
1:
git init
git status
git add .
git commit -m "Set up package"
git remote add origin https://github.com/Qiaozf/Stat302.Proj3.git
git push -u origin master
git push -u origin master: push your local changes to origin
```
```
2.```{r}
#Write a function my_t.test() that performs a one sample t-test in R. To prove it works, use or simulate any data. Use this data for a two-sided t-test using both my_t.test() and t.test(). The results should match. Do the same for a one-sided t-test.

#Your function should return a list with elements:

#test_stat: the numeric test statistic.
#df: the degrees of freedom.
#alternative: the value of the parameter alternative.
#p_val: the numeric p-value.

library("tidyverse")
```


```{r}
3:
# Load "mtcar"
data(mtcars)

## Function: my_lm Return a table of information includes "Estimate","Std. Error","t value","Pr(>|t|)" in the form of table
#            It's a brief combination of lm() and summary()
# Input: regression formula, data frame
# Output: A table includes related data
```


```{r}
4:
# Load libaray and data
library(tidyverse)
library(class)
library(randomForest)
data("iris")
set.seed(302)


# Function: my_knn_cv. Predict given class by using covariats sepal.(length, width)
#                      and petal.(length, width) 
# Input: a data frame, true class value of training data
#        an integer representing the number of neighbors
#        an integer representing the number of folds
# Output: A list which consists of a vector that includes all observations and a vector
#         than includes numeric data.
```


```{r}
5:
# Function: my_rf_cv  Predict output sepal.length using covariates sepal.with
#                     and petal.(width, length)
# Input: a numeric number stands for number of folds
# Output: a number -- the cross-valiadation error
```
